Age-related changes in plant growth and traits

### 2015-12-18 Accessory_figs_2015_12.Rmd
continuing accessory cost analyses; trying to add in calcs for prepollenation costs - still in progress

```{r}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
SummaryInd$costs_for_seed <- SummaryInd$seed_count * SummaryInd$seedcosts
SummaryInd$costs_for_aborted <- SummaryInd$repro_inv - SummaryInd$costs_for_seed
plot(costs_for_seed ~ costs_for_aborted,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
SummaryInd$prop_aborted <- SummaryInd$costs_for_aborted / SummaryInd$repro_inv
plot(prop_aborted ~ age, data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="x")

plot(costs_for_seed ~ repro_inv,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
abline(0,1)

par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
xvar <- "costs_for_aborted"
yvar <- "costs_for_seed"

@@

par(mfrow=c(1,3), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(propagule_inv~total_weight_0,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
mod <- lm(log(total_weight_0)~log(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
words.top.left.logxy(mod)

@@

#shift in accessory costs per seed with seed size
par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
win.metafile("figs2/accessory_per_seed_vs_seed_size.wmf", height=6, width=6)
plot
plot(accessory_per_seed~seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
points(accessory_per_seed~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)
summary(mod)
abline(log(5),1)
dev.off()

@@

```{r}
par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(accessory_per_seed~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(accessory_inv~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(seedset~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(seedset~costs_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="y")
plot(accessory_per_seed~costs_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="y")
plot(propagule_inv~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(propagule_inv~repro_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(propagule_inv~total_weight,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(repro_inv~total_weight,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
abline(0,1)
```

>>>>

```{r}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.5,.5)) 
plot(costs_for_seed ~ seed_size,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
points(costs_for_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
mod <- lm(log(seed_size) ~ log(costs_for_seed),data=subset(SummarySpp[["mean"]])) 
words.top.left.logxy(mod)

plot(costs_for_aborted ~ seed_size,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
points(costs_for_aborted ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
mod <- lm(log(seed_size) ~ log(costs_for_aborted),data=subset(SummarySpp[["mean"]])) 
words.top.left.logxy(mod)

plot(accessory_inv ~ seed_size,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
points(accessory_inv ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
mod <- lm(log(seed_size) ~ log(accessory_inv),data=subset(SummarySpp[["mean"]])) 
words.top.left.logxy(mod)
abline(mod)

plot(costs_for_seed ~ costs_for_aborted,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
points(costs_for_seed ~ costs_for_aborted,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
mod <- lm(log(costs_for_seed) ~ log(costs_for_aborted),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)

plot(costs_for_seed ~ repro_inv,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
abline(0,1)
```

SummaryInd$prop_costs_seed <- SummaryInd$costs_for_seed / SummaryInd$repro_inv
SummaryInd$prop_costs_aborted <- SummaryInd$costs_for_aborted / SummaryInd$repro_inv

```{r}
win.metafile("figs2/acc_cost_seed_size.wmf", height=6, width=6)

plot
plot(prepollencosts~seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy",cex=1.3)
mod <- lm(log(seed_size)~log(accessory_costs),data=subset(SummaryInd))
words.top.left.logxy(mod)
abline((log(10)^coef(mod)[1]),coef(mod)[2])
abline((log(10)^coef(mod)[1]),1,col="red")

summary(mod)
dev.off()
```

plot(seedset~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy",cex=1)
points(seedset~accessory_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
mod <- lm(log(accessory_costs)~log(seedset),data=subset(SummaryInd,seedset>0))
words.bottom.left.logxy(mod)
abline((log(10)^coef(mod)[1]),(coef(mod)[2]))
abline((log(10)^coef(mod)[1]),-1,col="red")

summary(mod)

@@

par(mfrow=c(1,3), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(propagule_inv~total_weight_0,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(total_weight_0)~log(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
words.top.left.logxy(mod)

@@

#shift in accessory costs per seed with seed size
par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
win.metafile("figs2/accessory_per_seed_vs_seed_size.wmf", height=6, width=12)
plot
plot(costs_per_seed~seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
points(costs_per_seed~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
mod <- lm(log(seed_size)~log(costs_per_seed),data=subset(SummarySpp[["mean"]]))
words.top.left.logxy(mod)
summary(mod)

plot(seedcosts~seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy",cex=1.3)
mod <- lm(log(seed_size)~log(seedcosts),data=subset(SummaryInd))
words.top.left.logxy(mod)
dev.off()

@@

```{r}
#par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))

```

```{r}
plot(accessory_inv~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(seedset~seedcosts,data=subset(SummaryInd,seedset>0),col=col.spp(species),pch=16,log="x")
plot(seedset~costs_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="x")
plot(packaging_dispersal_inv~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(propagule_inv~repro_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(propagule_inv~total_weight,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(repro_inv~total_weight,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
abline(0,1)
```
